Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-15 latex/comp_or.tex
Starting to change paper to multiprocess

Below, we present four implementations for $SolveNode$: {\it Ant Colony Optimization}\/ (ACO), {\it Multiprocessed Ant Colony Optimization}\/ ({\it mpACO}),  and {\it Shims},  and {\it Multiprocessed Shims (mpShims)}.

It is important to say that the parallel ACO ({\it pACO}) is a different implementation where employs threads instead of processes to solve each ant solution in parallel. We chose {\it mpACO} for our approach because of the need to share the pheromone array between ants/processes and the facility to handle the possibility of race condition.

\subsubsection{Ant Colony Optimization (ACO)}

@@

	\caption{ $SolveNode(ACO, k, G)$ } \label{alg:aco}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets Greedy(k, G, 1)$  \label{aco:greedy}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets 4$ \label{aco:ants}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{($stagnant < 3$) {\bf and} ($runtime < 0.7s$)} \label{aco:while}
			\For{$a \gets 1$ to $A$} \label{aco:g1}
				\State $G^a(V_k, E^{Na}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
				\State $E \gets \{ (p_i,t^k_j) \mid (p_i,t^k_j) \not\in E^{Na}_k \}$
				\While{$|E| > 0$}
					\State $e \gets Roulette(E)$ biased through $ga^k_{ij}$  \label{aco:roulette}
					\State $E \gets E - \{e\}$		
					\If{$E^{Na}_k \cup \{e\}$ is feasible}
						\State $ E^{Na}_k \gets E^{Na}_k \cup \{e\} $ \label{aco:ant2}
					\EndIf	
				\EndWhile	
				\If{$f_s(G^{a}) > f_s(G^{+})$} \label{aco:gen1}
					\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^a(V_k, E^{Na}_k \cup E^Q_k)$  \label{aco:gen2}
						\For{each $(p_i,t^k_j) \in E^{N+}_k$}
							\State $\tau^k_{ij} \gets \tau^k_{ij} - \Delta\tau^k_{ij}$ \label{aco:phero1}
							\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga1}
						\EndFor
				\EndIf 
			\EndFor \label{aco:g2}
			\If{$f_s(G^+) > f_s(G^*)$} \label{aco:best1}
				\State $stagnant \gets 0$
				\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
				\For{each $(p_i,t^k_j) \in E^{N*}_k$}
					\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho1}
					\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau^k_{ij}$ \label{aco:phero2}
					\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga2}
				\EndFor			
			\Else
				\State $stagnant \gets stagnant + 1$ \label{aco:best2}
			\EndIf
			\For{all $\tau^k_{ij}$} 
				\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho2}
			\EndFor	
		\EndWhile	
		\State ${\bf return}$ $G^*(V_k, E^{N*}_k \cup E^Q_k)$		
	\end{algorithmic}
\end{algorithm}

@@

\subsubsection{Shims}

Finally, we present a new heuristic designed specifically for ACLP+RPDP, which we named \emph{Shims}. Like in mechanics, shims are collections of spacers to fill gaps, which may be composed of parts with different thicknesses (see Figure \ref{fig:shims}). This strategy is based on a practical observation: usually, subsets of smaller and lighter items are saved for later adjustments to the remaining clearances.

@@

Communication between processes can be achieved via {\it multiprocessing.Queue} and {\it multiprocessing.Pipe} which permits regular inter-process communication -IPC. (https://uwpce-pythoncert.github.io/Py300/threading-multiprocessing.html)

>>>>

Below, we present 2 implementations for $SolveNode$: {\it Multiprocess Ant Colony Optimization}\/ ({\it mpACO})  and a new parallel heuristic that we propose called {\it Multiprocess Shims (mpShims)}.

It is important to say that the parallel ACO ({\it pACO}) is a different implementation where employs threads instead of processes to solve each ant solution in parallel (for a detailed information on parallel ACO see \cite{Pedemonte2011}). We chose {\it mpACO} for our approach because of the need to share the pheromone array between ants/processes and the facility to handle the possibility of race condition.

\subsubsection{Multiprocess Ant Colony Optimization (mpACO)}

@@

	\caption{ $SolveNode(mpACO, k, G)$ } \label{alg:aco}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets Greedy(k, G, 1)$  \label{aco:greedy}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets$ a number of ants or parallel processes to be determined for each iteration \label{aco:ants}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{($stagnant < 3$) {\bf and} ($runtime < 0.7s$)} \label{aco:while}

		\State $publish$
		\State $solutions \gets subscribe()$

			\For{$a \gets 1$ to $A$} \label{aco:g1}
				\State $G^a(V_k, E^{Na}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
				\State $E \gets \{ (p_i,t^k_j) \mid (p_i,t^k_j) \not\in E^{Na}_k \}$
				\While{$|E| > 0$}
					\State $e \gets Roulette(E)$ biased through $ga^k_{ij}$  \label{aco:roulette}
					\State $E \gets E - \{e\}$		
					\If{$E^{Na}_k \cup \{e\}$ is feasible}
						\State $ E^{Na}_k \gets E^{Na}_k \cup \{e\} $ \label{aco:ant2}
					\EndIf	
				\EndWhile	
				\If{$f_s(G^{a}) > f_s(G^{+})$} \label{aco:gen1}
					\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^a(V_k, E^{Na}_k \cup E^Q_k)$  \label{aco:gen2}
						\For{each $(p_i,t^k_j) \in E^{N+}_k$}
							\State $\tau^k_{ij} \gets \tau^k_{ij} - \Delta\tau^k_{ij}$ \label{aco:phero1}
							\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga1}
						\EndFor
				\EndIf 
			\EndFor \label{aco:g2}
			\If{$f_s(G^+) > f_s(G^*)$} \label{aco:best1}
				\State $stagnant \gets 0$
				\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
				\For{each $(p_i,t^k_j) \in E^{N*}_k$}
					\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho1}
					\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau^k_{ij}$ \label{aco:phero2}
					\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga2}
				\EndFor			
			\Else
				\State $stagnant \gets stagnant + 1$ \label{aco:best2}
			\EndIf
			\For{all $\tau^k_{ij}$} 
				\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho2}
			\EndFor	
		\EndWhile	
		\State ${\bf return}$ $G^*(V_k, E^{N*}_k \cup E^Q_k)$		
	\end{algorithmic}
\end{algorithm}

@@

\subsubsection{Multiprocess Shims - mpShims}

Finally, we present a new heuristic designed specifically for ACLP+RPDP, which we named \emph{mpShims}. Like in mechanics, shims are collections of spacers to fill gaps, which may be composed of parts with different thicknesses (see Figure \ref{fig:shims}). This strategy is based on a practical observation: usually, subsets of smaller and lighter items are saved for later adjustments to the remaining clearances.

@@

Communication between processes can be achieved via {\it multiprocessing.Queue} and {\it multiprocessing.Pipe} which permits regular inter-process communication -IPC. (\cite{multiprocessing}).
